Allocate landings to Georges Bank EPU

### 2021-02-22 docs/SimData.Rmd

>>>>

The MSSPM needs diet compostion information as well. Here we supply two survey time series of diet data, one census and a trial survey dataset with more typical survey coverage issues.

```{r, write-msspm-diet}

all_diets <- read_savedsurvs(d.name, 'survDiet')

# aggregate over ages (survey diet is in proportion by age)

trueB_age_allbox <- NOBAom_ms$truebio_ss %>%
  #sum over polygons
  aggregate(dat$atoutput,list(dat$species,dat$agecl,dat$time, dat$prey),sum)

### 2021-02-22 docs/allocateLandingsEPU.Rmd

```{r GBfoot, eval=T}
crs <- 4326
# NEW GB EPU def based on survey strata
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","GB_SOE_strata.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs)

@@

-   The `offshoreWind` package then uses these rasters combined with commerical fishing data (DMIS) to determine the landings assigned to any spatial footprint supplied. This is achieved by calculating the overlap of the rasters with the user supplied spatial footprint.

@@

```{r calc_props_sp, eval=T, out.width="100%"}
source(here::here("data-raw","plot_landings_proportions.r"))
plot_landings_proportions(species="cols")

@@

```{r calc_props_st, eval=T, out.width="100%"}
plot_landings_proportions(species="rows")

@@

```{r calc_lands,  eval=T, out.width="100%"}
source(here::here("data-raw","plot_landings.r"))
plot_landings()

>>>>

```{r GBfoot, eval=T, fig.cap="Georges Bank EPU", fig.align='center'}
crs <- 4326
# NEW GB EPU def based on survey strata
coast <- sf::st_read(here::here("gis", 'NES_LME_coast.shp'), quiet = T) %>%
  sf::st_transform(.,crs=crs)
GB_strata <- sf::st_read(here::here("gis","GB_SOE_strata.shp"),quiet=T) %>%
    sf::st_transform(.,crs=crs)

@@

-   The `offshoreWind` package then uses these rasters combined to determine the landings assigned to any spatial footprint supplied. This is achieved by calculating the overlap of the rasters with the user supplied spatial footprint.

@@

```{r calc_props_sp, eval=T, out.width="100%",fig.align='center',fig.cap="Proportion of landings in GB relative to statistical area"}
source(here::here("data-raw","plot_landings_proportions.r"))
plot_landings_proportions(species="cols")

@@

```{r calc_props_st, eval=T, out.width="100%",fig.align='center',fig.cap="Proportion of landings in GB relative to statistical area"}
plot_landings_proportions(species="rows")

@@

```{r calc_lands,  eval=T, out.width="100%",fig.align='center',fig.cap="Total landings by statistical area"}
source(here::here("data-raw","plot_landings.r"))
plot_landings()
